A Simple Minibatch Acceptance Test for MCMC

### 2016-05-18 nips_2016.tex
revise the xp

In this section, we explore the convergence properties of our algorithm.  Define our estimate of
$X_{\rm norm}$ as $X_{\rm norm}'$, and let $X_{\xi} = X_{\rm norm} - X_{\rm norm}'$, so that
$\Delta' = \Delta + X_{\rm norm} + X_\xi$.  We also denote $F_X$ as the CDF of $X$.  Let the
transition kernel of complete data at sampling step $i$ be $T_i$, and let the transition kernel of
minibatch data at sampling step $i$ is $T_i'$.  We show that the distance of $T_i$ and $T_i'$ is
proportional to our estimate error $X_{\xi}$. We also define the stationary distribution obtained
by $T_i$ is $\pi$.  We show the by decreasing the step size, the distribution of our sampled data
converges to $\pi$. We use something called the \emph{total variation distance} between two kernels,
denoted as $\| \cdot \|$.

@@

Since the accuracy of our transition kernel is related to the accuracy of our $X_{\rm norm}$
estimate, we can show that error of our estimation is roughly proportional to the step size of our
proposer.

@@

Since ${\rm Var}(\Delta') < \epsilon^2 k^2 m $, we can assume the maximum value of $X_{\xi}$ is
proportional to the standard deviation of $\Delta$, i.e. $\epsilon$. Thus, we can assume
$\zeta=\epsilon C$, where $C$ is a constant factor.

>>>>

In this section, we explore the convergence properties of our algorithm.  Define our estimate of
$X_{\rm norm}$ as $X_{\rm norm}'$, and let $X_{\xi} = X_{\rm norm} - X_{\rm norm}'$, so that
$\Delta' = \Delta + X_{\rm norm} + X_\xi$. We assume the standard derivation of $X_{\rm norm}$ is less than $\pi/\sqrt{3}$, so that we can always apply deconvolution process in Eq~\cite{eq:deconvolution} without using a temperature. We also denote $F_X$ as the CDF of $X$.  Let the
transition kernel of complete data at sampling step $i$ be $T_i$, and let the transition kernel of
minibatch data at sampling step $i$ is $T_i'$.  We show that the distance of $T_i$ and $T_i'$ is
proportional to our estimate error $X_{\xi}$. We also define the stationary distribution obtained
by $T_i$ is $\pi$.  We show the by decreasing the step size, the distribution of our sampled data
converges to $\pi$. We use something called the \emph{total variation distance} between two kernels,
denoted as $\| \cdot \|$.

@@

Thus, the accuracy of our transition kernel is related to the accuracy of our $X_{\rm norm}$
estimate. We now show that error of our estimation is roughly proportional to the step size of our proposer.

@@

Since ${\rm Var}(\Delta') < \epsilon^2 k^2 m $, we can assume the maximum value of $X_{\xi}$ is
proportional to the standard deviation of $\Delta'$, i.e. $\epsilon$. Thus, we can assume
$\zeta=\epsilon C$, where $C$ is a constant factor.
